---
title: "HW2_House_Matthew"
author: "Matthew House"
date: "9/11/2017"
output:
  pdf_document: default
  fig_caption: yes
  fig_height: 6
  fig_width: 7
  classoption: landscape
header-includes: \setlength\parindent{24pt} \usepackage{MnSymbol} \usepackage{mathrsfs}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs n such, echo=FALSE}
#initialize and load libraries
    rm(list = ls())   
    graphics.off()
    options(scipen = 4, digits = 6)
    options(stringsAsFactors = FALSE)
    knitr::opts_chunk$set(echo = F, eval=T, cache=T, tidy.opts=list(width.cutoff=55),
                tidy=T, include=FALSE, message=F, warning=F)
    library.warn <- library
    library <- function(package, help, pos = 2, lib.loc = NULL, character.only = FALSE,
                        logical.return = FALSE, warn.conflicts = FALSE, quietly = TRUE,
                        verbose = getOption("verbose")) {
       if (!character.only) {
          package <- as.character(substitute(package))
       }
       suppressPackageStartupMessages(library.warn(
          package, help, pos, lib.loc, character.only = TRUE,
          logical.return, warn.conflicts, quietly, verbose))}
    #setwd("~/Google Drive/Projects/....")

    #install.packages("scatterplot3d")
    #library(scatterplot3d)
    #install.packages("car")
    #library(car)
    #library(doParallel)
    #setup parallel backend to use 7 processors
    #no_cores <- detectCores() - 2
    #cl<-makeCluster(no_cores)
    #registerDoParallel(cl)
    #stopCluster(cl)
    #library(MASS)
    #library(RColorBrewer)
    #library(plot3D)
    #install.packages("tidyverse") ##kinda overkill, only need dplyr and tidyr
    library(tidyverse)
    #library(beeswarm)
    #library(stargazer)
    #library(data.table)
    #library(lubridate)
```

    Problem 4
   
    When creating programs or code that is ongoing over multiple classes, having a
    version control system allows you to review your progress. So if at some point
    your code stops working like it is supposed to you can go back to the newest
    version that was working without having to start from scratch. If reviewing for
    a final exam or compiling for a final project, having specific pieces to refer
    to can be helpful, especially if you were diligently commenting as you went.
    
Problem 5
  
```{r problem 5 part A, echo=FALSE, include=TRUE}
url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/Sensory.dat"
    my_sensory <- read.table(url, header = F, skip = 1, fill = T, stringsAsFactors = F)
    my_tidy_sensory <- my_sensory[-1,]
    #below renames the variables from row 1 
    my_tidy_sensory_a <- my_tidy_sensory %>% filter(V1 %in% 1:10) %>%
            rename(Item = V1, V1 = V2, V2 = V3, V3 = V4, V4 = V5, V5 = V6)
    #below creates characters as opposed to numeric values
    my_tidy_sensory_b <- filter(.data = my_tidy_sensory, !(V1 %in% 1:10)) %>%
            mutate(Item = rep(as.character(1:10), each = 2)) %>%
            mutate(V1 = as.numeric(V1)) %>%
            select(c(Item, V1:V5))
    #line below rejoins the two datasets we separated above 
    my_tidy_sensory <- bind_rows(my_tidy_sensory_a, my_tidy_sensory_b)
    #below gives column names Person_1 through Person_5
    colnames(my_tidy_sensory) <- c("Item", paste("Person", 1:5, sep = "_"))
    #line below is to update the data frame
    my_tidy_sensory <- my_tidy_sensory %>%
        gather(Person, value, Person_1:Person_5) %>%
        mutate(Person = gsub("Person_", "", Person)) %>%
        arrange(Item)


knitr::kable(summary(my_tidy_sensory), caption="Sensory data summary")

```




```{r}
url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/Sensory.dat"
    Sensory_raw<-read.table(url, header=F, skip=1, fill=T, stringsAsFactors = F)
    Sensory_tidy<-Sensory_raw[-1,]
    Sensory_tidy_a<-filter(.data = Sensory_tidy,V1 %in% 1:10) %>%
                    rename(Item=V1,V1=V2,V2=V3,V3=V4,V4=V5,V5=V6)
    Sensory_tidy_b<-filter(.data = Sensory_tidy,!(V1 %in% 1:10)) %>%
                    mutate(Item=rep(as.character(1:10),each=2)) %>%
                    mutate(V1=as.numeric(V1)) %>%
                    select(c(Item,V1:V5))
    Sensory_tidy<-bind_rows(Sensory_tidy_a,Sensory_tidy_b)
    colnames(Sensory_tidy)<-c("Item",paste("Person",1:5,sep="_"))
    Sensory_tidy<-Sensory_tidy %>%  
        gather(Person,value,Person_1:Person_5) %>%  
        mutate(Person = gsub("Person_","",Person)) %>%
        arrange(Item)
```

