---
title: "HW5_House_Matthew"
author: "Matthew House"
date: "10/3/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("tidyr")
library(tidyr)
library(dplyr)
library(ggplot2)
library(knitr)
```

#### Problem 1

Completed

#### Problem 2

Completed

#### Problem 3

What are you thoughts for what makes a good figure?

    * A good figure is informative and can convey, on its own, what the author is attempting to say. It should clearly separate variables as well as display a difference between classes of displayed data. Using the correct scales is important as is showing the full range of the graphed data. Clipping data to make the results seem more poignant is misleading. 
    
#### Problem 4  

a. Create a function that computes the proportion of successes in a vector.  Use good programming practices.

```{r vector function, echo=T, include=T, eval=T}
# this  was taken from "https://www.r-bloggers.com/r-function-of-the-day-tapply-2/" and edited to work for this problem
 my_vect <-
    data.frame(patient = 1:100,
               age = rnorm(100, mean = 60, sd = 12),
               treatment = gl(2, 50,
                 labels = c("Treatment", "Control")),
               success = sample(c(0,1), replace = TRUE, size = 100))

lapply(my_vect[4:4], mean)
#This is a randomly generated value vector so the probability of a success changes each time you run it.

#tapply(flags$animate, flags$landmass, mean)
```

b. Create a matrix to simulate 10 flips of a coin with varying degrees of "fairness" as follows:

```{r echo=T, include=T, eval=F}

    set.seed(12345)
    P4b_data <- matrix(rbinom(10, 1, prob = (30:40)/100), nrow = 10, ncol = 10)

```

c. Use your function in conjunction with apply to compute the proportion of success in P4b_data by column and then by row.  What do you observe?  What is going on? 

    * It reads it a long vector without row and column designations... unless I didn't do something correctly.

```{r echo=T, include=T, eval=F}

#P4b_data




```


d. You are to fix the above matrix by creating a function whose input is a probability and output is a vector whose elements are the outcomes of 10 flips of a coin.  Now create a vector of the desired probabilities.  Using the appropriate apply family function, create the matrix we really wanted above.  Prove this has worked by using the function created in part a to compute and tabulate the appropriate marginal successes.

```{r echo=T, include=T, eval=F}
ht <- function(){
  coin_flips <- sample(1:2, size = 10, replace = TRUE)
  return(c(coin_flips))
}
ht()
# Couldn't figure out how to use the apply functions without changing this to have row and column names. 
Heads_or_Tails <- replicate(10, ht())
table(Heads_or_Tails)
table(Heads_or_Tails)/length(Heads_or_Tails)
```

## Problem 5

Load, munge, and explore the data given in Wu and Hamada from the starch experiment.  Consider strength as the response.  You do not need to form a model or otherwise analyze the dataset, you do need to explore the data, make any figures/tables necessary to make observations about the data, and generally annotate the process in text.  

<http://www2.isye.gatech.edu/~jeffwu/book/data/starch.dat>

```{r echo=T, include=T, eval=T}

url<- "http://www2.isye.gatech.edu/~jeffwu/book/data/starch.dat"
starch <- read.table(url, header = F, skip = 1, fill = T, stringsAsFactors = F)
TidyStarch <- transmute(.data = starch, Starch = V1, Strength = V2, Thickness = V3)
head(TidyStarch)

grouped <-  group_by(TidyStarch,Starch)
ggplot(grouped, aes(x = Thickness, y = Strength, colour = Starch)) +
  geom_point() +
    geom_smooth(method='lm',formula=y~x)
#+
#  facet_wrap( ~ starch)

```


## Problem 6

Our ultimate goal in this problem is to create an annotated map of the US.  I am giving you the code to create said map, you will need to customize it to include the annotations.

Part a. Get and import a database of US cities and states.  Here is some R code to help:

```{r get_city_list, echo=T, eval=F, include=T}

    #we are grabbing a SQL set from here
    # http://www.farinspace.com/wp-content/uploads/us_cities_and_states.zip

    #download the files, looks like it is a .zip
#    install.packages("downloader")
    library(downloader)
    download("http://www.farinspace.com/wp-content/uploads/us_cities_and_states.zip",dest="us_cities_states.zip")
    unzip("us_cities_states.zip", exdir="./")
    
    #read in data, looks like sql dump, blah
    library(data.table)
    states <- fread(input = "./us_cities_and_states/states.sql",skip = 23,sep = "'", sep2 = ",", header = F, select = c(2,4))
    ### YOU do the CITIES
    ### I suggest the cities_extended.sql may have everything you need
    ### can you figure out how to limit this to the 50?
    
```

Part b. Create a summary table of the number of cities included by state.

```{r echo=T, include=T, eval=F}

cities <- fread(input = "./us_cities_and_states/cities_extended.sql", sep = "'", sep2 = ",", header = F, select = c(2,4))
 
 colnames(states) <- c("State Name", "State Abbv.")
 colnames(cities) <- c("City", "State Abbv.")
 
 citystate <- inner_join(cities, states, by = "State Abbv.")
 
 statesum = table(citystate$`State Name`)
 Numcitystate = as.data.frame(statesum)
 
 colnames(Numcitystate) <- c("State Name", "Freq")
 
knitr::kable(Numcitystate)

#This was used from Shane's code, as I couldn't get it to count the
#way I was doing it. 





```


Part c. Create a function that counts the number of occurances of a letter in a string.  The input to the function should be "letter" and "state_name".  The output should be a scalar with the count for that letter.



Create a for loop to loop through the state names imported in part a.  Inside the for loop, use an apply family function to iterate across a vector of letters and collect the occurance count as a vector.

```{r echo=T, eval=F, include=T}

    ##pseudo code
    letter_count <- data.frame(matrix(NA,nrow=50, ncol=26))
    getCount <- function(){
        temp <- strsplit(state_name)
        # how to count??
        return(count)
    }
    for(i in 1:50){
        letter_count[i,] <- xx-apply(args)
    }
```

Part d.

Create 2 maps to finalize this.  Map 1 should be colored by count of cities on our list within the state.  Map 2 should highlight only those states that have more than 3 occurances of ANY letter in thier name.


Quick and not so dirty map:

```{r eval=F, echo=T, include=T}
    #https://cran.r-project.org/web/packages/fiftystater/vignettes/fiftystater.html
    library(ggplot2)
#   install.packages("fiftystater")
#   install.packages("mapproj")
    library(fiftystater)
    library(mapproj)
    
    data("fifty_states") # this line is optional due to lazy data loading
    crimes <- data.frame(state = tolower(rownames(USArrests)), USArrests)
    # map_id creates the aesthetic mapping to the state name column in your data
    p <- ggplot(crimes, aes(map_id = state)) + 
      # map points to the fifty_states shape data
      geom_map(aes(fill = Assault), map = fifty_states) + 
      expand_limits(x = fifty_states$long, y = fifty_states$lat) +
      coord_map() +
      scale_x_continuous(breaks = NULL) + 
      scale_y_continuous(breaks = NULL) +
      labs(x = "", y = "") +
      theme(legend.position = "bottom", 
            panel.background = element_blank())
    
    p
    #ggsave(plot = p, file = "HW5_Problem6_Plot_Settlage.pdf")
```
## Problem 7

Push your homework and submit a pull request.

**When it is time to submit, --ONLY-- submit the .Rmd and .pdf solution files.  Names should be formatted HW4_lastname_firstname.Rmd**



