---
title: "HW4_House_Matt"
author: "Matthew House"
date: "9/26/2017"
output: pdf_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# install.packages("readxl")    
# install.packages("rJava")
#install.packages("dplyr")
#install.packages("tidyr")
#install.packages("ggplot2")
#install.packages("plotly")
library(dplyr)
library(tidyr)
library(ggplot2)
library(plotly)
library(readxl)

```

####Problem 3: 

In the lecture, there were a few links to Exploratory Data Analysis (EDA) materials.  According to Roger Peng, what is the focus of the EDA stage of an analysis?  Hint: this is summarized in the free sample portion of his online book.

  * According to Roger Peng, the focus of the EDA stage of an analysis is to identify what is important and what can be cut out. He relates this to a film editing room, where the director and others can pair different scenes to see which group tells the most complete story relative to the script. He notes that this stage is important to keep the the project moving forward. 
  
####Problem 4:

```{r, echo=T, eval=T, include=T}

    prob4_data1 <- read_excel("HW4_data.xlsx", sheet = 1, col_names = TRUE)
    prob4_data2 <- read_excel("HW4_data.xlsx", sheet = 2, col_names = TRUE)

mydata <- rbind(prob4_data1, prob4_data2)

summydata <- mydata %>%
        group_by(block) %>%
        summarise_all(funs(mean,sd)) %>%

        arrange()
         
knitr::kable(summydata, caption="Summary Statistics")

```

```{r factor exploration, echo=T, eval=T, include=T}

    prob4_data1 <- read_excel("HW4_data.xlsx", sheet = 1, col_names = TRUE)
    prob4_data2 <- read_excel("HW4_data.xlsx", sheet = 2, col_names = TRUE)
   
mydata <- rbind(prob4_data1, prob4_data2)

grouped <-  group_by(mydata,block)
          
ggplot(grouped, aes(x = phosphate, y = depth, colour = block)) +
  geom_point() +
  facet_wrap( ~ block)


```

Factors that appear to be present are within groups and plotting depth against phosphate produces shapes for some of the groups and groups of lines for others. 

```{r correlation plots, echo=T, eval=T, include=T}

   prob4_data1 <- read_excel("HW4_data.xlsx", sheet = 1, col_names = TRUE)
    prob4_data2 <- read_excel("HW4_data.xlsx", sheet = 2, col_names = TRUE)

mydata <- rbind(prob4_data1, prob4_data2)

summydata <- mydata %>%
        group_by(block) %>%
        summarise_all(funs(mean,sd, median, cor(phosphate,depth, 
                  use = "pairwise.complete.obs", method = "pearson"))) %>%
        transmute(block, depth_mean, phosphate_mean, 
                  depth_sd, phosphate_sd, 
                  depth_median, phosphate_median, 
                  Correlation = depth_cor) %>%
        arrange()

pairs(summydata[2:3], main = "Blocks",
      pch = 21, bg = summydata$block[unclass(summydata$block)],
      panel=function(x, y, ...) { points(x, y, ...); 
      text(x, y,) })
    
     

        
knitr::kable(summydata, caption="Summary Statistics")

```

Using groups allowed me to see shapes. I don't know what I am missing for the pairs plots. I didn't see anything that jumped out at me. Perhaps the way that I am doing it is wrong. 

#### Problem 5

For problem 4, is there a single most illuminating figure that shows a key component of the data??  This is the figure you should use as your first submission in next weeks contest.  Save it as a pdf and make sure it is ready for pushing at the start of class. (Torg 1100, try to be a little early)  What did this exercise show you?  

Just seaparating the groups showed a distinct difference in what the plots looked like. 

```{r interesting plot, echo=T, eval=T, include=T}
#Sys.setenv("plotly_username"="wynne")
Sys.setenv("plotly_api_key"="X8YHpLYCaQrYJ1IvTqKk")

#install.packages("webshot")
#webshot::install_phantomjs()

    prob4_data1 <- read_excel("HW4_data.xlsx", sheet = 1, col_names = TRUE)
    prob4_data2 <- read_excel("HW4_data.xlsx", sheet = 2, col_names = TRUE)
   
mydata <- rbind(prob4_data1, prob4_data2)

grouped <-  group_by(mydata,block)
          
ggplot(grouped, aes(x = depth, y = phosphate, colour = block)) +
  geom_point() +
  facet_wrap( ~ block)

block1 <- grouped[which(grouped$block == "1"),]
density1 <- density(block1$phosphate)

block2 <- grouped[which(grouped$block == "2"),]
density2 <- density(block2$phosphate)

block3 <- grouped[which(grouped$block == "3"),]
density3 <- density(block3$phosphate)

block4 <- grouped[which(grouped$block == "4"),]
density4 <- density(block4$phosphate)

block5 <- grouped[which(grouped$block == "5"),]
density5 <- density(block5$phosphate)

block6 <- grouped[which(grouped$block == "6"),]
density6 <- density(block6$phosphate)

block7 <- grouped[which(grouped$block == "7"),]
density7 <- density(block7$phosphate)

block8 <- grouped[which(grouped$block == "8"),]
density8 <- density(block8$phosphate)

block9 <- grouped[which(grouped$block == "9"),]
density9 <- density(block9$phosphate)

block10 <- grouped[which(grouped$block == "10"),]
density10 <- density(block10$phosphate)

block11 <- grouped[which(grouped$block == "11"),]
density11 <- density(block11$phosphate)

block12 <- grouped[which(grouped$block == "12"),]
density12 <- density(block12$phosphate)

block13 <- grouped[which(grouped$block == "13"),]
density13 <- density(block13$phosphate)



p <- plot_ly(x = ~density1$x, y = ~density1$y, type = 'scatter', mode = 'lines', name = 'Phosphate1', fill = 'tozeroy') %>%
  
  add_trace(x = ~density2$x, y = ~density2$y, name = 'Phosphate2', fill = 'tozeroy') %>%
  
  add_trace(x = ~density3$x, y = ~density3$y, name = 'Phosphate3', fill = 'tozeroy') %>%
 
  add_trace(x = ~density4$x, y = ~density4$y, name = 'Phosphate4', fill = 'tozeroy') %>%
  
  add_trace(x = ~density5$x, y = ~density5$y, name = 'Phosphate5', fill = 'tozeroy') %>%
  
  add_trace(x = ~density6$x, y = ~density6$y, name = 'Phosphate6', fill = 'tozeroy') %>%
  
  add_trace(x = ~density7$x, y = ~density7$y, name = 'Phosphate7', fill = 'tozeroy') %>%
  
  add_trace(x = ~density8$x, y = ~density8$y, name = 'Phosphate8', fill = 'tozeroy') %>%
  
  add_trace(x = ~density9$x, y = ~density9$y, name = 'Phosphate9', fill = 'tozeroy') %>%
  
  add_trace(x = ~density10$x, y = ~density10$y, name = 'Phosphate10', fill = 'tozeroy') %>%
  
  add_trace(x = ~density11$x, y = ~density11$y, name = 'Phosphate11', fill = 'tozeroy') %>%
  
  add_trace(x = ~density12$x, y = ~density12$y, name = 'Phosphate12', fill = 'tozeroy') %>%
  
  add_trace(x = ~density13$x, y = ~density13$y, name = 'Phosphate13', fill = 'tozeroy') %>%

  layout(xaxis = list(title = 'Phosphate'),
         yaxis = list(title = 'Density')) 


block1a <- grouped[which(grouped$block == "1"),]
density1a <- density(block1a$depth)
block2a <- grouped[which(grouped$block == "2"),]
density2a <- density(block2a$depth)
block3a <- grouped[which(grouped$block == "3"),]
density3a <- density(block3a$depth)
block4a <- grouped[which(grouped$block == "4"),]
density4a <- density(block4a$depth)
block5a <- grouped[which(grouped$block == "5"),]
density5a <- density(block5a$depth)
block6a <- grouped[which(grouped$block == "6"),]
density6a <- density(block6a$depth)
block7a <- grouped[which(grouped$block == "7"),]
density7a <- density(block7a$depth)
block8a <- grouped[which(grouped$block == "8"),]
density8a <- density(block8a$depth)
block9a <- grouped[which(grouped$block == "9"),]
density9a <- density(block9a$depth)
block10a <- grouped[which(grouped$block == "10"),]
density10a <- density(block10a$depth)
block11a <- grouped[which(grouped$block == "11"),]
density11a <- density(block11a$depth)
block12a <- grouped[which(grouped$block == "12"),]
density12a <- density(block12a$depth)
block13a <- grouped[which(grouped$block == "13"),]
density13a <- density(block13a$depth)

p2 <- plot_ly(x = ~density1a$x, y = ~density1a$y, type = 'scatter', mode = 'lines', name = 'Depth1', fill = 'tozeroy') %>%

  add_trace(x = ~density2a$x, y = ~density2a$y, name = 'Depth2', fill = 'tozeroy') %>%

  add_trace(x = ~density3a$x, y = ~density3a$y, name = 'Depth3', fill = 'tozeroy') %>%  
  
  add_trace(x = ~density4a$x, y = ~density4a$y, name = 'Depth4', fill = 'tozeroy') %>%
  
  add_trace(x = ~density5a$x, y = ~density5a$y,  name = 'Depth5', fill = 'tozeroy') %>%

  add_trace(x = ~density6a$x, y = ~density6a$y,  name = 'Depth6', fill = 'tozeroy') %>%  

  add_trace(x = ~density7a$x, y = ~density7a$y, name = 'Depth7', fill = 'tozeroy') %>%  
  
  add_trace(x = ~density8a$x, y = ~density8a$y, name = 'Depth8', fill = 'tozeroy') %>%

  add_trace(x = ~density9a$x, y = ~density9a$y, name = 'Depth9', fill = 'tozeroy') %>%  

  add_trace(x = ~density10a$x, y = ~density10a$y, name = 'Depth10', fill = 'tozeroy') %>%      
    
  add_trace(x = ~density11a$x, y = ~density11a$y, name = 'Depth11', fill = 'tozeroy') %>% 
 
  add_trace(x = ~density12a$x, y = ~density12a$y, name = 'Depth12', fill = 'tozeroy') %>%
  
  add_trace(x = ~density13a$x, y = ~density13a$y, name = 'Depth13', fill = 'tozeroy') %>%  

  layout(xaxis = list(title = 'Depth'),
         yaxis = list(title = 'Density'))  
   
export(subplot(p, p2), "areafill2.pdf")



p1 <- plot_ly(grouped, x = ~phosphate, y = ~depth, color = ~block, type = "scatter", mode = "markers") 
p2 <- plot_ly(grouped, x = ~phosphate, y = ~depth, color = ~block, type = "scatter", mode = "markers") 
#p3 <- plot_ly(grouped, x = ~phosphate, y = ~depth, color = ~block, type = "scatter", mode = "markers") 
#p4 <- plot_ly(grouped, x = ~phosphate, y = ~depth, color = ~block, type = "scatter", mode = "markers") 
export(subplot(p1, p2), "subplots.pdf")

export(plot_ly(grouped, x = ~phosphate, y = ~depth, color = ~block, type = "scatter", mode = "markers"), "plot.pdf")


plot_ly(grouped, type = "scatter3d", x = ~block , y = ~depth , z = ~phosphate, color = ~block, mode = "markers" )


plot_ly(grouped, x = ~phosphate, y = ~depth, type = "scatter", mode = "markers", color = ~block)
  
#  , "plot3.pdf")

plot_ly(grouped, x = ~phosphate, y = ~depth, color = I("red")) %>%
add_lines() %>%
add_markers(color = ~block) %>%
layout(showlegend = TRUE)



```


```{r eval=F, echo=T, include=T, results='asis', tidy=F}
######################################################
######################################################
############ END OF HOMEWORK #########################
######################################################
######################################################

### We will have a more detailed plotting discussion
### and do the following 2 data sets next week
```

